%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%     File: Thesis_Acknowledgments.tex                                 %
%     Tex Master: Thesis.tex                                           %
%                                                                      %
%     Author: Andre C. Marta                                           %
%     Last modified :  2 Jul 2015                                      %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{\acknowledgments}

% Add entry in the table of contents as section
\addcontentsline{toc}{section}{\acknowledgments}

%A few words about the university, financial support, research advisor, dissertation readers, faculty or other professors, lab mates, other friends and family...

I would like to express my sincere thanks to my supervisor Ricardo Gon\c calo for his support, invaluable scientific advise and inspirational enthusiasm, without which this work would not have been concluded. To my co-supervisor, Pedro Abreu, I thank for ...

I acknowledge the funding of this research by Funda\c cao para a Ci\^encia e Tecnologia - FCT, through ...

I am very thankful to Patricia Conde and Rute Pedro for fruitful discussions and very helpful advise. To my master colleagues in the LIP ATLAS group, Aidan Kelly, Ant\'onio Costa and Ricardo Barru\'e, I thank for the companionship and motivation throughout this journey. 

I am thankful to Duarte Azevedo, Pedro Ferreira and Rui Santos for being our on-call theoreticians, always available to help.   

I would like to thank all my colleagues in the LIP ATLAS group for making me feel very welcome. I extend my gratitude to everybody at LIP for making it a fantastic place to work. I would also like to acknowledge the LIP IT and secretariat for their patience and technical support.

I would like to thank my boyfriend, Jo\~ao Augusto, for his never ending patience and unconditional support. To my friends of Chafarrica I express my most sincere thanks for always being a great support, source of joy and laughter. 

To my sister I thank for always welcoming me home with a smile, for the numerous time she offered to help and for all the memes that lighten up some of my days.

To my parents, I will never be able to thank enough. I thank them for their love, unconditional support, inspiration, help in times of need ... . 
