%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     File: ExtendedAbstract_imple.tex                               %
%     Tex Master: ExtendedAbstract.tex                               %
%                                                                    %
%     Author: Andre Calado Marta                                     %
%     Last modified : 27 Dez 2011                                    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A Calculation section represents a practical development
% from a theoretical basis.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The FCC-hh and the baseline detector}
\label{sec:detFCC}
 
The FCC-hh baseline design consist of a of a proton-proton circular collider with a maximum CM energy of $\sqrt{s}=100$ TeV housed by a $100$ km tunnel in the area of Geneva. It will deliver a peak luminosity of $\mathcal{L}=30\times 10^{34}~\text{cm}^{-2}\text{s}^{-1}$ in its ultimate phase which will result in a $O(30)~\text{ab}^{-1}$ per experiment. This machine will extend the research program of the LHC (and of the HL-LHC) after these have reached their full discovery potential, by around 2040.

The design of the FCC-hh baseline detector has been greatly based on that of the ATLAS and CMS experiments, in particular the central barrel. The layers and sub detectors are arranged in the same order and perform very similar roles. The ID detector covers the pseudorapidity range $|\eta|<6$ and it will be instrumented with pixel and strip detectors. The ECAL covers the pseudorapidity range $|\eta|<6$. The proposed layout is a LAr sampling configuration with lead, glue and steal plates as absorbers. The granularity is expected to be two to four times better than for the ATLAS ECAL. The hadronic calorimeter covers the pseudorapidity range $|\eta| < 6$. It is divided in barrel, end-cap and forward that cover the pseudorapidity ranges $|\eta| < 1.3$, $1.0 < |\eta| < 1.8$ and $2.3 < |\eta| < 6.0$. For the barrel and end-cap calorimeters, the expected segmentation $\Delta\eta\times\Delta\phi = 0.025 \times 0.025$ while for the forward calorimeter it is $\Delta\eta\times\Delta\phi = 0.05 \times 0.05$. Overall, this corresponds to approximately four times the ATLAS HCAL granularity. The MS cover the pseudorapidity range $|\eta|<6$ and it consists of a layered structure of gas chambers.